---
title: "Results cleaned"
author: "CLEMOT Bastien"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Results for D. minor male courtship behaviour ~ female mating state

### Packages and data importation:

```{r}
# Packages:
library(tidyverse)
library(Hmisc)
library(car)
library(lme4)
library(performance)
library(AICcmodavg)
library(gridExtra)
library(plotrix)


# Datasets:
subset1 <- read.table("subset1_Bastien_original_weight.csv",sep=",",header=T)
subset2 <- read.table("subset2_Bastien_original_weight.csv",sep=",",header=T)
data <- rbind(subset1,subset2)
```


### Total courtship duration ~ Female Mating state (1)

```{r}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=total.courtship.duration, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Total courtship duration (s)") +
  ggtitle("Total courtship duration depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

### Number of courtship segments ~ Female Mating state (1)

```{r}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=number.of.courtships, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Number of courtship segments") +
  ggtitle("Number of courtship attempts depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

### Mean duration of courtship segments ~ Female Mating state (1)

```{r}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=mean.courtship.length, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Mean length of courtship segments (s)") +
  ggtitle("Mean length of courtship segments depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```


### Male getting killed ~ Female Mating State (4)

```{r}
# Fuse data for pre and post copulatory kill
data$Male.killed <- data$pre.copulatory.kill | data$post.copulatory.kill
# Graphical representation
ggplot(data, aes(fill=Male.killed,x=femalematedbefore)) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  geom_bar() +
  theme_minimal() +
  xlab("Female mating state")
```

### Standardise data

```{r}
# Standardise data:
data$std.number.of.courtships <- scale(data$number.of.courtships,center=TRUE,scale=TRUE)
data$std.total.courtship.duration <- scale(data$total.courtship.duration,center=TRUE,scale=TRUE)
data$std.mean.courtship.length <- scale(data$mean.courtship.length,center=TRUE,scale=TRUE)
```


### Number of attacks ~ Female Mating State * Male courtship (4)

```{r Complete model}
# Complete model
mod.attk <- glmer(number.of.attacks ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data)
Anova(mod.attk,type='II')
summary(mod.attk)
```

```{r VIF}
# Calculate VIF
# Obtain VIF:
vif(mod.attk)
# Create a better model:
mod.attk2 <- glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data)
# Obtain VIF:
vif(mod.attk2)
```

```{r AIC}
# Find best model based on AIC:
AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.total.courtship.duration + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore-std.total.courtship.duration + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ 1 + (1|Female),family = poisson,data=data))
```

```{r Final model}
# Keep the best model
mod.attk3 <- glmer(number.of.attacks ~ femalematedbefore*std.number.of.courtships + (1|Female),family = poisson,data=data)
Anova(mod.attk3,type='II')
summary(mod.attk3)
```

### Mean time of mounting ~ Female Mating State * Male courtship (4) 

```{r Complete model}
# Creation of model:
mod.mount <- lmer(mean.mount.length ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),data=data)
summary(mod.mount)
Anova(mod.mount,type='II')
```

```{r VIF}
# Obtain VIF:
vif(mod.mount)
```

```{r AIC}
# Find the best model based on AIC:
AIC(lmer(mean.mount.length ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.total.courtship.duration + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore*std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore*std.number.of.courtships + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore*std.total.courtship.duration + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ (1|Female),data=data))
```

```{r Final model}
summary(mod.mount)
Anova(mod.mount,type='II')
```


### Number of attacks ~ Female Mating State & Number of flees ~ Female Mating State & Correlation (3) 

```{r Number of attacks}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=number.of.attacks, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Number of attacks") +
  ggtitle("Number of attacks from the females depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

```{r Number of flees}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=number.of.flees, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Number of flees") +
  ggtitle("Number of flees from the males depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

```{r Correlation}
cor.test(data$number.of.attacks,data$number.of.flees,method = "spearman") 
cor.test(data$number.of.attacks,data$number.of.courtships,method = "spearman") 
cor.test(data$number.of.flees,data$number.of.courtships,method = "spearman")
plot(data$number.of.attacks,data$number.of.courtships)
```

 

### Number of courtships/flees/attacks ~ Male condition (5)

```{r Preparation}
df <- subset1
colnames(df)[56] <- "Male.last.weight1"
df.maleratio <- left_join(df[,c("Female","Male.last.weight1")],subset2[,c("number.of.attacks","number.of.courtships","number.of.flees","Female","Male.last.weight")])
df.maleratio$maleratio <- df.maleratio$Male.last.weight1/df.maleratio$Male.last.weight
```

```{r Number of courtships}
mod1 <- lm(number.of.courtships ~ maleratio ,data=df.maleratio)
summary(mod1)
Anova(mod1,type='II')
```

```{r Number of attacks}
mod2 <- lm(number.of.attacks ~ maleratio ,data=df.maleratio)
summary(mod2)
Anova(mod2,type='II')
```

```{r Number of flees}
mod3 <- lm(number.of.flees ~ maleratio ,data=df.maleratio)
summary(mod3)
Anova(mod3,type='II')
```



### Courtship parameters ~ Female agressiveness (2) 

```{r Total courtship duration}
mod.tot <- lmer(total.courtship.duration ~ femalematedbefore*number.of.attacks + (1|Female),data=data)
summary(mod.tot)
Anova(mod.tot,type='II')
```

```{r Number of courtships}
mod.nb <- glmer(number.of.courtships ~ femalematedbefore+number.of.attacks + (1|Female),family = poisson,data=data)
summary(mod.nb)
Anova(mod.nb,type='II')
```

### copy
```{r Number of courtships}
mod.nbé <- glm(number.of.courtships ~ femalematedbefore*number.of.attacks,family = poisson,data=data)
summary(mod.nbé)
Anova(mod.nb,type='II')
```

```{r Mean courtship duration}
mod.mean <- lmer(mean.courtship.length ~ femalematedbefore*number.of.attacks + (1|Female),data=data)
summary(mod.mean)
Anova(mod.mean,type='II')
```







### Test of my outcomes models by removing the outlier:

```{r data set without the outlier}
data2 <- data[-21,]
subset1bis <- subset1[-6,]
subset2bis <- subset2[-6,]
```

```{r Total courtship duration}
mod.tot2 <- lmer(total.courtship.duration ~ femalematedbefore+number.of.attacks + (1|Female),data=data2)
summary(mod.tot2)
Anova(mod.tot2,type='II')
```

```{r Number of courtships}
mod.nb2 <- glmer(number.of.courtships ~ femalematedbefore + number.of.attacks + (1|Female),family = poisson,data=data2)
summary(mod.nb2)
Anova(mod.nb2,type='II')
```


### Test for courtship timing parameters between the two groups:

```{r}
# test for latency to attack:
wilcox.test(subset1$latency.to.attack,subset2$latency.to.attack,paired=TRUE)
ggplot(data, aes(x=femalematedbefore, y=as.numeric(latency.to.attack), fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Latency to attack (s)") +
  ggtitle("Latency to attack depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

```{r}
# test for latency to mount:
wilcox.test(subset1$latency.to.mount,subset2$latency.to.mount,paired=TRUE)
mean(subset1$latency.to.mount)
mean(subset2$latency.to.mount,na.rm=TRUE)
ggplot(data, aes(x=femalematedbefore, y=as.numeric(latency.to.mount), fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Latency to mount (s)") +
  ggtitle("Latency to mount depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

```{r}
# Test for latency to touch:
wilcox.test(subset1$latency.to.touch,subset2$latency.to.touch,paired=TRUE)
mean(subset1$latency.to.touch,na.rm=TRUE)
mean(subset2$latency.to.touch,na.rm=TRUE)
ggplot(data, aes(x=femalematedbefore, y=as.numeric(latency.to.touch), fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Latency to touch (s)") +
  ggtitle("Latency to touch depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

```{r}
# Test for latency to attack:
wilcox.test(subset1$latency.to.attack,subset2$latency.to.attack,paired=TRUE)
mean(subset1$latency.to.attack,na.rm=TRUE)
mean(subset2$latency.to.attack,na.rm=TRUE)
ggplot(data, aes(x=femalematedbefore, y=as.numeric(latency.to.attack), fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("lightgray","gray30")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Latency to attack (s)") +
  ggtitle("Latency to attack depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```



### Timing of courtship ~ Female mating status, barplots of mean

```{r}
# Total coursthip duration
means <- c(mean(subset1$total.courtship.duration),mean(subset2$total.courtship.duration))
st.errors <- c(std.error(subset1$total.courtship.duration),std.error(subset2$total.courtship.duration))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA

# number of courthip attempts
means <- c(mean(subset1$number.of.courtships),mean(subset2$number.of.courtships))
st.errors <- c(std.error(subset1$number.of.courtships),std.error(subset2$number.of.courtships))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotB <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotB

# Mean courtship duration
means <- c(mean(subset1$mean.courtship.length),mean(subset2$mean.courtship.length))
st.errors <- c(std.error(subset1$mean.courtship.length),std.error(subset2$mean.courtship.length))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotC <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotC
```
```{r}
testA <- subset1[,c("Female","mean.courtship.length")]
testB <- subset2[,c("Female","mean.courtship.length")]
colnames(testB) <- c("Female","mean.courtship.length2")
testC <- left_join(testA,testB)
wilcox.test(testC$mean.courtship.length,testC$mean.courtship.length2,paired=TRUE)
```
```{r}
testA <- subset1[,c("Female","total.courtship.duration")]
testB <- subset2[,c("Female","total.courtship.duration")]
colnames(testB) <- c("Female","total.courtship.duration2")
testC <- left_join(testA,testB)
wilcox.test(testC$total.courtship.duration,testC$total.courtship.duration2,paired=TRUE)
```
```{r}
testA <- subset1[,c("Female","number.of.courtships")]
testB <- subset2[,c("Female","number.of.courtships")]
colnames(testB) <- c("Female","number.of.courtships2")
testC <- left_join(testA,testB)
wilcox.test(testC$number.of.courtships,testC$number.of.courtships2,paired=TRUE)
```



### Some other parameters of courthip:

```{r}
# latency.to.mount
testA <- subset1[,c("Female","latency.to.mount")]
testB <- subset2[,c("Female","latency.to.mount")]
colnames(testB) <- c("Female","latency.to.mount2")
testC <- left_join(testA,testB)
wilcox.test(testC$latency.to.mount,testC$latency.to.mount2,paired=TRUE)

means <- c(mean(subset1$latency.to.mount,na.rm=TRUE),mean(subset2$latency.to.mount,na.rm=TRUE))
st.errors <- c(std.error(subset1$latency.to.mount),std.error(subset2$latency.to.mount))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# latency.to.attack
testA <- subset1[,c("Female","latency.to.attack")]
testB <- subset2[,c("Female","latency.to.attack")]
colnames(testB) <- c("Female","latency.to.attack2")
testC <- left_join(testA,testB)
wilcox.test(testC$latency.to.attack,testC$latency.to.attack2,paired=TRUE)

means <- c(mean(subset1$latency.to.attack,na.rm=TRUE),mean(subset2$latency.to.attack,na.rm=TRUE))
st.errors <- c(std.error(subset1$latency.to.attack),std.error(subset2$latency.to.attack))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# latency.to.touch
testA <- subset1[,c("Female","latency.to.touch")]
testB <- subset2[,c("Female","latency.to.touch")]
colnames(testB) <- c("Female","latency.to.touch2")
testC <- left_join(testA,testB)
wilcox.test(testC$latency.to.touch,testC$latency.to.touch2,paired=TRUE)

means <- c(mean(subset1$latency.to.touch,na.rm=TRUE),mean(subset2$latency.to.touch,na.rm=TRUE))
st.errors <- c(std.error(subset1$latency.to.touch),std.error(subset2$latency.to.touch))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# number.of.attacks
testA <- subset1[,c("Female","number.of.attacks")]
testB <- subset2[,c("Female","number.of.attacks")]
colnames(testB) <- c("Female","number.of.attacks2")
testC <- left_join(testA,testB)
wilcox.test(testC$number.of.attacks,testC$number.of.attacks2,paired=TRUE)

means <- c(mean(subset1$number.of.attacks,na.rm=TRUE),mean(subset2$number.of.attacks,na.rm=TRUE))
st.errors <- c(std.error(subset1$number.of.attacks),std.error(subset2$number.of.attacks))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# latency.to.copulate
testA <- subset1[,c("Female","latency.to.copulate")]
testB <- subset2[,c("Female","latency.to.copulate")]
colnames(testB) <- c("Female","latency.to.copulate2")
testC <- left_join(testA,testB)
wilcox.test(testC$latency.to.copulate,testC$latency.to.copulate2,paired=TRUE)

means <- c(mean(subset1$latency.to.copulate,na.rm=TRUE),mean(subset2$latency.to.copulate,na.rm=TRUE))
st.errors <- c(std.error(subset1$latency.to.copulate),std.error(subset2$latency.to.copulate))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# number.of.courtships
testA <- subset1[,c("Female","number.of.courtships")]
testB <- subset2[,c("Female","number.of.courtships")]
colnames(testB) <- c("Female","number.of.courtships2")
testC <- left_join(testA,testB)
wilcox.test(testC$number.of.courtships,testC$number.of.courtships2,paired=TRUE)

means <- c(mean(subset1$number.of.courtships,na.rm=TRUE),mean(subset2$number.of.courtships,na.rm=TRUE))
st.errors <- c(std.error(subset1$number.of.courtships),std.error(subset2$number.of.courtships))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# total.mount.duration
testA <- subset1[,c("Female","total.mount.duration")]
testB <- subset2[,c("Female","total.mount.duration")]
colnames(testB) <- c("Female","total.mount.duration2")
testC <- left_join(testA,testB)
wilcox.test(testC$total.mount.duration,testC$total.mount.duration2,paired=TRUE)

means <- c(mean(subset1$total.mount.duration,na.rm=TRUE),mean(subset2$total.mount.duration,na.rm=TRUE))
st.errors <- c(std.error(subset1$total.mount.duration),std.error(subset2$total.mount.duration))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# number.of.mounts
testA <- subset1[,c("Female","number.of.mounts")]
testB <- subset2[,c("Female","number.of.mounts")]
colnames(testB) <- c("Female","number.of.mounts2")
testC <- left_join(testA,testB)
wilcox.test(testC$number.of.mounts,testC$number.of.mounts2,paired=TRUE)

means <- c(mean(subset1$number.of.mounts,na.rm=TRUE),mean(subset2$number.of.mounts,na.rm=TRUE))
st.errors <- c(std.error(subset1$number.of.mounts),std.error(subset2$number.of.mounts))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

```{r}
# mean.mount.length
testA <- subset1[,c("Female","mean.mount.length")]
testB <- subset2[,c("Female","mean.mount.length")]
colnames(testB) <- c("Female","mean.mount.length2")
testC <- left_join(testA,testB)
wilcox.test(testC$mean.mount.length,testC$mean.mount.length2,paired=TRUE)

means <- c(mean(subset1$mean.mount.length,na.rm=TRUE),mean(subset2$mean.mount.length,na.rm=TRUE))
st.errors <- c(std.error(subset1$mean.mount.length),std.error(subset2$mean.mount.length))
df.tot <- data.frame(group = c('unmated','mated'),mean = means, se = st.errors)
plotA <- ggplot(df.tot) +
  geom_bar(aes(x=group, y=mean),stat="identity") +
  scale_x_discrete(limits = c('unmated','mated')) +
  geom_errorbar( aes(x=group, ymin=mean-se, ymax=mean+se), width=0.4, colour="orange", alpha=0.9, size=1.3)
plotA
```

