---
title: "Dolomedes minor male courtship - Data Analysis"
author: "CLEMOT Bastien"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Packages:
library(tidyverse)
library(Hmisc)
library(car)
library(lme4)
library(performance)
library(AICcmodavg)


# Datasets:
subset1 <- read.table("subset1_Bastien_original_weight.csv",sep=",",header=T)
subset2 <- read.table("subset2_Bastien_original_weight.csv",sep=",",header=T)
data <- rbind(subset1,subset2)
```

# Is male courtship changing depending on female mating state?

Differences between the two groups (virgin;mated) were assessed with three indicators of male courtship: total courtship duration, number of courtship segments, mean courtship segment length.

As all data were paired and, as a counting variable was used, it was decided to only use non-parametric test for paired data.
Wilcoxon paired test were performed to assess differences between means.
Differences between variance were also assessed by using a jackknife test.

### Jackknife function (Rothstein et William, 1981):

```{r}
# Used dataset should have 3 columns, first with female ID, second with variable for the first mating trial (virgin) and third with the variable in the second mating trial (mated).

# Function for the jackknife:
jackknife <- function(dataset) {
  # Calculate variance of variable X
  varX <- 0
  for (i in 1:nrow(dataset)) {
    varX <- varX + (dataset[i, 3] - mean(dataset[, 3])) ^ 2
  }
  # Calculate variance of variable Y
  varY <- 0
  for (i in 1:nrow(dataset)) {
    varY <- varY + (dataset[i, 2] - mean(dataset[, 2])) ^ 2
  }
  # Calculate y, ratio of variances
  y <- varY / varX
  # Calculate all y-i
  dataset$yi <- NA
  for (i in 1:nrow(dataset)) {
    varXi <- 0
    varYi <- 0
    dataseti <- dataset[-i, ]
    for (j in 1:(nrow(dataset) - 1)) {
      varXi <- varXi + (dataseti[j, 3] - mean(dataseti[, 3])) ^ 2
      varYi <- varYi + (dataseti[j, 2] - mean(dataseti[, 2])) ^ 2
    }
    dataset[i, 4] <- varYi / varXi
  }
  # Logarithmic transformation of all y-i
  dataset$Li <- nrow(dataset) * log(y) - (nrow(dataset) - 1) * log(dataset$yi)
  # Calculate mean of the distribution (mean of all y-i)
  meanL <- mean(dataset$Li)
  # Calculate variance of distribution (variance of all y-1)
  vLi <- 0
  for (i in 1:nrow(dataset)) {
    vLi <- vLi + (dataset[i, 5] - mean(dataset[, 5])) ^ 2
  }
  VarLi <- vLi / (nrow(dataset) * (nrow(dataset) - 1))
  # Calculate Q the statistical value
  Q <- meanL / sqrt(VarLi)
  return(Q)
}
```

## Total courtship duration:

```{r}
# Wilcoxon paired test:
wilcox.test(subset1bis$total.courtship.duration,subset2bis$total.courtship.duration,paired=TRUE)
```
p-value > 0.05: no significant differences in mean between both groups.

```{r message=FALSE}
# Jackknife variance test:
dataset <- subset1bis[,c("Female","total.courtship.duration")]
colnames(dataset)[2] <- "virgin"
dataset <- left_join(dataset,subset2bis[,c("Female","total.courtship.duration")])
colnames(dataset)[3] <- "mated"
```

```{r}
jackknife(dataset)
```

Statistical value of -1.61 gives a p-value of 0.053 > 0.05: no significant differences in variance between two groups.

```{r}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=total.courtship.duration, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("darkolivegreen1","#FFBBFF")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Total courtship duration (s)") +
  ggtitle("Total courtship duration depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```


## Number of courtship segments:

```{r warning=FALSE}
# Wilcoxon paired test:
wilcox.test(subset1bis$number.of.courtships,subset2bis$number.of.courtships,paired=TRUE)
```
p-value > 0.05: no significant differences in mean between two groups.

```{r}
# Jackknife variance test:
dataset <- subset1bis[,c("Female","number.of.courtships")]
colnames(dataset)[2] <- "virgin"
dataset <- left_join(dataset,subset2bis[,c("Female","number.of.courtships")])
colnames(dataset)[3] <- "mated"
```
```{r}
jackknife(dataset)
```

Statistical value of -3.84 gives a p-value of 0.00006 <<< 0.05: significant difference of variance between two groups.

```{r}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=number.of.courtships, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("darkolivegreen1","#FFBBFF")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Number of courtship segments") +
  ggtitle("Number of courtship attempts depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```


## Mean courtship segment length:

```{r}
# Wilcoxon paired test:
wilcox.test(subset1bis$mean.courtship.length,subset2bis$mean.courtship.length,paired=TRUE)
```
p-value > 0.05: no significant differences in mean between two groups.

```{r}
# Jackknife variance test:
dataset <- subset1bis[,c("Female","mean.courtship.length")]
colnames(dataset)[2] <- "virgin"
dataset <- left_join(dataset,subset2bis[,c("Female","mean.courtship.length")])
colnames(dataset)[3] <- "mated"
```
```{r}
jackknife(dataset)
```

Statistical value of -0.61 give a p-value of 0.27 > 0.05: no significant differences in variance between two groups.

```{r}
# Graphical representation:
ggplot(data, aes(x=femalematedbefore, y=mean.courtship.length, fill=femalematedbefore)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  scale_fill_manual(values=c("darkolivegreen1","#FFBBFF")) +
  xlab("Female mating state") +
  scale_x_discrete(labels = c("Virgin","Mated")) +
  ylab("Mean length of courtship segments (s)") +
  ggtitle("Mean length of courtship segments depending on female mating state") +
  theme_minimal() +
  theme(legend.position="none")
```

# As a trade-OFF between signals and behaviours that are used to increase male survival chances

To assess wich response to courtship should be investigated between all parameters, correlation test were performed.

Mixed model linear regression were performed between each quantitative parameter used to assess female aggressiveness and parameters used to assess male decisions in courtship and female mating state.
Variance Inflation Factor was calculated to select pertinent explaining variables and AIC was calculated to select models. When performing mixed model linear regression, Female ID was used as a random effect and qualitative fixed effect were standardised to have the same scale.

For qualitative parameters, distribution McNemar's chi square tests were performed with female mating state.

## Correlation tests between parameters:

```{r}
data$Male.killed <- data$pre.copulatory.kill | data$post.copulatory.kill
cor(data[,c("number.of.attacks","number.of.flees","Male.killed","latency.to.attack")],method = "spearman", use = "complete.obs")
cor.test(data$latency.to.attack,data$number.of.attacks,method = "spearman")
```
Any of those parameters show an import correlation.

## Male getting killed:

```{r}
# Creation of contingency table:
Male.killed <- table(subset1$pre.copulatory.kill|subset1$post.copulatory.kill,subset2$pre.copulatory.kill|subset2$post.copulatory.kill,dnn=list("virgin","mated"))
Male.killed

# McNemar's chi square test:
mcnemar.test(Male.killed)
```
p-value > 0.05: distribution is not significantly heterogeneous, males are not more often killed by virgin females than mated females

## Standardise data

```{r}
# Standardise data:
data$std.number.of.courtships <- scale(data$number.of.courtships,center=TRUE,scale=TRUE)
data$std.total.courtship.duration <- scale(data$total.courtship.duration,center=TRUE,scale=TRUE)
data$std.mean.courtship.length <- scale(data$mean.courtship.length,center=TRUE,scale=TRUE)
```

## Number of attacks:

```{r}
# Creation of model:
mod.attk <- glmer(number.of.attacks ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data)
summary(mod.attk)
Anova(mod.attk,type='II')
```

```{r}
# Obtain VIF:
vif(mod.attk)
# Create a better model:
mod.attk2 <- glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data)
# Obteain VIF:
vif(mod.attk2)
```

```{r warning=FALSE}
# Find best model based on AIC:

AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + femalematedbefore*std.total.courtship.duration + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ femalematedbefore-std.total.courtship.duration + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.attacks ~ 1 + (1|Female),family = poisson,data=data))
```

So we want to keep the 6th model, with only the number of courtships.

```{r}
# Keep the best model
mod.attk3 <- glmer(number.of.attacks ~ femalematedbefore:std.number.of.courtships + (1|Female),family = poisson,data=data)
Anova(mod.attk3,type='II')
summary(mod.attk3)
```

## Number of flees:

```{r}
# Creation of model:
mod.flees <- glmer(number.of.flees ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.total.courtship.duration + femalematedbefore*std.mean.courtship.length + (1|Female),family = poisson,data=data)
Anova(mod.flees,type='II')
summary(mod.flees)
```
```{r}
# Obtain VIF:
vif(mod.flees)
```

```{r warning=FALSE}
# Find best model based on AIC:
AIC(glmer(number.of.flees ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.total.courtship.duration + femalematedbefore:std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.flees ~ femalematedbefore:std.total.courtship.duration + femalematedbefore:std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.flees ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.flees ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.total.courtship.duration + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.flees ~ femalematedbefore:std.mean.courtship.length + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.flees ~ femalematedbefore:std.number.of.courtships + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.flees ~ femalematedbefore:std.total.courtship.duration + (1|Female),family = poisson,data=data))
AIC(glmer(number.of.flees ~ 1 + (1|Female),family = poisson,data=data))
```
We want to keep the 6th one

```{r}
mod.flees2 <- glmer(number.of.flees ~ femalematedbefore:std.number.of.courtships + (1|Female),family = poisson,data=data)
summary(mod.flees2)
```

## Latency to attack:

```{r}
# Creation of model:
mod.lat.attk <- glmer(latency.to.attack ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.total.courtship.duration + femalematedbefore:std.mean.courtship.length + (1|Female),family = gaussian,data=data)
summary(mod.lat.attk)
```

```{r}
# Obtain VIF:
vif(mod.lat.attk)
```

So we want to remove the std.total.courtship.duration

```{r message=FALSE}
# Remove femalematedbefore:std.total.courtship.duration:
mod.lat.attk2 <- lmer(latency.to.attack ~ femalematedbefore*std.number.of.courtships + femalematedbefore*std.mean.courtship.length + (1|Female),data=data)
summary(mod.lat.attk2)
Anova(mod.lat.attk2,type='II')
```
```{r}
# Obtain VIF:
vif(mod.lat.attk2)
```
```{r message=FALSE}
# Find the best model based on AIC:
AIC(lmer(latency.to.attack ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(latency.to.attack ~ femalematedbefore:std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(latency.to.attack ~ femalematedbefore:std.number.of.courtships + (1|Female),data=data))
AIC(lmer(latency.to.attack ~ (1|Female),data=data))
```
So we want to keep the first model

```{r}
summary(mod.lat.attk2)
```

# and risk for sperm competition

Same method as previous part was applied.

## Copulation success of individuals:

```{r}
# Creation of contingency table:
table(subset1$copulation,subset2$copulation,dnn = list("virgin","mated"))
Copulation <- matrix(c(0, 11, 0, 4),nrow = 2,dimnames = list("1st Survey" = c("False", "True"),"2nd Survey" = c("False", "True")))
Copulation

# McNemar's chi square test:
mcnemar.test(Copulation)
```
p-value < 0.05: distribution is significantly not homogeneous, mating trials with virgin females have a more important reproduction success.

## Mean time of mounting

```{r}
# Creation of model:
mod.mount <- lmer(mean.mount.length ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.total.courtship.duration + femalematedbefore:std.mean.courtship.length + (1|Female),data=data)
summary(mod.mount)
```
```{r}
# Obtain VIF:
vif(mod.mount)
```
```{r}
# Find the best model based on AIC:
AIC(lmer(mean.mount.length ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.total.courtship.duration + femalematedbefore:std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore:std.total.courtship.duration + femalematedbefore:std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore:std.number.of.courtships + femalematedbefore:std.total.courtship.duration + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore:std.mean.courtship.length + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore:std.number.of.courtships + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ femalematedbefore:std.total.courtship.duration + (1|Female),data=data))
AIC(lmer(mean.mount.length ~ (1|Female),data=data))
```
We want to keep the first one

```{r}
summary(mod.mount)
```

### Number of attacks ~ Female Mating State & Number of flees ~ Female Mating State & Correlation

```{r}
# Number of attacks
# Wilcoxon paired test:
wilcox.test(subset1$number.of.attacks,subset2$number.of.attacks,paired=TRUE)
# Jacknife:
dataset <- subset1[,c("Female","number.of.attacks")]
colnames(dataset)[2] <- "virgin"
dataset <- left_join(dataset,subset2[,c("Female","number.of.attacks")])
colnames(dataset)[3] <- "mated"
jackknife(dataset) # P value of 0.03
# Number of flees
# Wilcoxon paired test:
wilcox.test(subset1$number.of.flees,subset2$number.of.flees,paired=TRUE)
# Jacknife:
dataset <- subset1[,c("Female","number.of.flees")]
colnames(dataset)[2] <- "virgin"
dataset <- left_join(dataset,subset2[,c("Female","number.of.flees")])
colnames(dataset)[3] <- "mated"
jackknife(dataset) # P value of 0.0401
# Correlation:
cor.test(data$number.of.attacks,data$number.of.flees,method = "spearman") # Correlation 
```

### Male condition 

```{r}
df <- subset1
colnames(df)[56] <- "Male.last.weight1"
df.maleratio <- left_join(df[,c("Female","Male.last.weight1")],subset2[,c("number.of.attacks","number.of.courtships","number.of.flees","Female","Male.last.weight")])
df.maleratio$maleratio <- df.maleratio$Male.last.weight1/df.maleratio$Male.last.weight
```

```{r}
# Effect on number of courtships
mod1 <- lm(number.of.courtships ~ maleratio ,data=df.maleratio)
summary(mod1)
Anova(mod1,type='II')
# Effect on number of attacks
mod2 <- lm(number.of.attacks ~ maleratio ,data=df.maleratio)
summary(mod2)
Anova(mod2,type='II')
# Effects on number of flees
mod3 <- lm(number.of.flees ~ maleratio ,data=df.maleratio)
summary(mod3)
Anova(mod3,type='II')
```

### Is male courtship influenced by female agressiveness or by another thing


```{r}
#### total.courtship.duration
mod.tot <- lmer(total.courtship.duration ~ femalematedbefore*number.of.attacks + (1|Female),data=data)
summary(mod.tot)
Anova(mod.tot,type='II')
#### number of courtships
mod.nb <- glmer(number.of.courtships ~ femalematedbefore*number.of.attacks + (1|Female),family = poisson,data=data)
summary(mod.nb)
Anova(mod.nb,type='II')
#### mean courtship duration
mod.mean <- lmer(mean.courtship.length ~ femalematedbefore*number.of.attacks + (1|Female),data=data)
summary(mod.mean)
Anova(mod.mean,type='II')
```

